Supplementary Materials And Methods

### 2020-10-30 Supplementary_fig_tab.Rmd
update supplements

---
title: "Supplementary Figures and Tables"
author: 
- Selcen Ari
- Alper Yilmaz 
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: NAR-sample.bib
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0}     \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{subfig}
  \usepackage{tabularx}
  \usepackage{caption}
---
\tableofcontents

@@

library(tidygraph)
library(dplyr)
library(tidyr)
library(stringr)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)
#knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(cache=FALSE)

@@

```{r, message=FALSE, warning=FALSE}
library(ceRNAnetsim)
```

@@

```{r}
# Sample dataset refers to minsamp in ceRNAnetsim package.
data("minsamp")
```

@@

@@

@@

|  Variable | Structure | Means 
|-----------|-----------|-------|
|  cluster    | character | Barcode from experimentally method |
|  chromosome    | character | Chromosome of Target gene from raw data |
|   start_position    | numeric | Gene start position from raw data |
|   end_position     | numeric | Gene end position from raw data |
|   strand     | character | Gene strand |
|   hgnc_symbol     | character | Gene name (Symbol) |
|   Ensembl_Gene_Id     | character | Ensembl Gene Id of gene |
|   Ensembl_Transcript_Id   | character | Ensembl transcript id of mRNA of Target gene |
|   target_seq   | character | mRNA sequences targeted by miRNA |
|   miRNA   | character | miRNA id (from miRBase version 21 ) |
|   miR_seq   | character | miRNA sequence |
|   seed_type   | character | seed type of miRNA:target interaction |
|   Energy   | numeric | Energy of miRNA:target binding |
|   HG38build_loc   | character | Recent chromosomal location of Gene |
|   Genome_build   | character| Genome build of given chromosome, start and end positions |
|   region   | character | interaction location on target | 
|   region_effect   | numeric | Coefficient of location on target | 
|   seed_type_effect   | numeric | Coefficient for seed sequence of miRNA:target interaction |

Table: miRNA:target pairs supported by High-throughput Experiments

>>>>

---
title: "Supplementary Figures and Tables"
author: 
- Selcen Ari
- Alper Yilmaz 
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: NAR-sample.bib
urlcolor: blue
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0}     \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{subfig}
  \usepackage{tabularx}
  \usepackage{caption}
---
\tableofcontents

@@

library(tidygraph)
library(dplyr)
library(tidyr)
library(stringr)
library(ggraph)
library(ggplot2)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)
#knitr::opts_chunk$set(fig.pos = 'H')
knitr::opts_chunk$set(cache=FALSE)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(ceRNAnetsim)
```

@@

```{r, echo=FALSE}
# Sample dataset refers to minsamp in ceRNAnetsim package.
data("minsamp")
```

@@

Interaction factors of Sample+ network are available in Table S1.

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.width=12, fig.height=5,fig.show='hold', fig.cap = "Tumor-specific perturbing nodes log2 transformed expression levels in tumor and normal tissue samples of 87 patients."}

matched_patient_exp_dataset <- readRDS("figures_manuscript/matched_patient_exp_dataset.RDS")
mirtarbase_gene_res <- readRDS("figures_manuscript/mirtarbase_gene_res.RDS")

matched_patient_exp_dataset%>%
  filter(Ensembl_Gene_Id %in% pull(filter(mirtarbase_gene_res, situ == "tumor_specific"), Ensembl_Gene_Id))%>%
  pivot_longer(cols = contains("TCGA"), names_to="patient_id", values_to = "expressions")%>%
  mutate(patient = ifelse(endsWith(patient_id, "01A"), "tumor", "normal"))%>%
  left_join(mirtarbase_gene_res, by ="Ensembl_Gene_Id")%>%
  group_by(patient, Ensembl_Gene_Id)%>%
  ggplot(aes(x= hgnc_symbol, y=log2(expressions), fill = patient))+
  #scale_y_log10()+
  geom_boxplot(position = "dodge")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90), panel.background = element_rect())+
  xlab("")
```

@@

|  Variable | Structure | Definition 
|-----------|-----------|-------|
|  cluster    | character | Barcode from experimentally method |
|  chromosome    | character | Chromosome of Target gene from raw data |
|   start_position    | numeric | Gene start position from raw data |
|   end_position     | numeric | Gene end position from raw data |
|   strand     | character | Gene strand |
|   hgnc_symbol     | character | Gene name (Symbol) |
|   Ensembl_Gene_Id     | character | Ensembl Gene Id of gene |
|   Ensembl_Transcript_Id   | character | Ensembl transcript id of mRNA of Target gene |
|   target_seq   | character | mRNA sequences targeted by miRNA |
|   miRNA   | character | miRNA id (from miRBase version 21 ) |
|   miR_seq   | character | miRNA sequence |
|   seed_type   | character | seed type of miRNA:target interaction |
|   Energy   | numeric | Energy of miRNA:target binding |
|   HG38build_loc   | character | Recent chromosomal location of Gene |
|   Genome_build   | character| Genome build of given chromosome, start and end positions |
|   region   | character | interaction location on target | 
|   region_effect   | numeric | Coefficient of location on target | 
|   seed_type_effect   | numeric | Coefficient for seed sequence of miRNA:target interaction |

Table: Context of miRNA:target pairs supported by High-throughput Experiments. CLEAR-CLiP and CLASH datasets were integrated as described in Section 2 of Supplementary Material and Method.

### 2020-10-30 Supplementary_mat_met.Rmd
update supplements

---
title: "Supplementary Materials And Methods"
author: 
- Selcen Ari
- Alper Yilmaz 
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: NAR-sample.bib
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0}     \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{subfig}
---
\tableofcontents

>>>>

---
title: "Supplementary Materials And Methods"
author: 
- Selcen Ari
- Alper Yilmaz 
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
  word_document: default
bibliography: NAR-sample.bib
urlcolor: blue
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0}     \renewcommand{\thefigure}{S\arabic{figure}}}
  \usepackage{subfig}
---
\tableofcontents
